Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-29 draft/paper1_jenny.tex
Edit 1-D profile

%    % TODO: The actual number waits to be updated}

@@

    Massive ETGs imaged at the depth of HSC are not well modeled by the de~Vaucouleurs
    or \ser law. 
    These models will fail to simultaneously describe the profile in both the inner and 
    the outer regions and also cannot account for any radial variations in ellipticity 
    and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
    the number of components, initial guesses of parameters, and the internal 
    degeneracies among different parameters. 
    Background subtraction uncertainty also affects the 2-D model fitting dramatically, 
    especially for massive ETGs in our sample. 
    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and measure their one-dimensional profiles of stellar mass surface 
    density (\mden{}). 
    This 1-D method we adopt is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not sensitive 
    to either the PSF ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).

    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask, and the PSF model. 
    These cut-outs include all of the light of the galaxy and are large enough to 
    also evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and Y band images (although these in principle may be better tracers of \mden{}).

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, we 
    use a customized procedure to detect and appropriately mask out neighbouring 
    objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To correct for this over-subtraction, we first aggressively mask all objects 
    (including the central massive galaxy), and derive an empirical background 
    correction using \texttt{SExtractor}.
    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
    following the methodology of \citet{Li2012}. 
    In short, we first fit each isophote using a free centroid and shape 
    (ellipticity and position angle). 
    We then fix the centroid (using the mean flux-weighted centroid) and estimate
    the mean ellipticity and position angles of all isophotes. 
    Finally, we extract a 1-D surface brightness profile along the major axis using 
    the mean ellipticity and position angle. 
    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, and integrate them to various radii to get the luminosity 
    within different physical (elliptical) apertures. 
    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z{\sim}0.2$ and also highlights 
    a few isophotes.

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to the uncertainty in the background subtraction. 
    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
    This is a conservative choice but already enables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    For more technical details of the \texttt{Ellipse} procedure, please see 
    Appendix~\ref{app:ellipse}.

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    \update{
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    }
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most major-merging massive galaxies.

    \update{
    Given our exquisite profiles that extend to 100 kpc, the definition and meaning of ``total'' 
    magnitude (and stellar mass) becomes more nuanced.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we integrate the profile to a range of radii, and estimate the stellar mass 
    within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:
    }

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
            builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and simulations 
            (e.g. \citealt{RodriguezGomez2016}), the in-situ component dominates the 
            \mstar{} within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc) of 
            $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the ``in-situ''
            phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over our 
            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
            0.3 and 0.5).

@@

\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Envelopes}

>>>>

@@

    The surface brightness profile of massive ETG can not be well modeled by the 
    de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
    These models will fail to simultaneously describe the profile in both the inner 
    and the outer regions and also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
    the number of components, initial guesses of parameters, and the internal 
    degeneracies among different parameters. 
    Background subtraction uncertainty also affects the 2-D model fitting 
    dramatically, especially for massive ETGs in our sample. 
    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and measure their one-dimensional profiles of stellar mass surface 
    density (\mden{}). 
    This 1-D method we adopt is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not 
    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
    ($r>100$ kpc).

    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask and the PSF model. 
    These cut-outs include all of the light of the galaxy and are large enough to 
    also evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
    we use a customized procedure to detect and aggressively mask out
    neighbouring objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To improve the background subtraction, we first aggressively mask 
    out all objects (including the central massive galaxy), and derive an 
    empirical background correction using \texttt{SExtractor}.
    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
    following the methodology of \citet{Li2012}. 
    In short, we first fit each isophote using a free centroid and shape 
    (ellipticity and position angle). 
    We then fix the centroid (using the mean flux-weighted centroid) and estimate
    the mean ellipticity and position angles of all isophotes. 
    Finally, we extract a 1-D surface brightness profile along the major axis using 
    the mean ellipticity and position angle. 
    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, and integrate them to various radii to get the luminosity 
    within different physical (elliptical) apertures. 
    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z{\sim}0.2$ and also highlights 
    a few isophotes.

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to either the uncertainty in the background 
    subtraction or the unmasked flux from other objects.
    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
    This is a conservative choice but already enables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    For more technical details of the \texttt{Ellipse} procedure, please see 
    Appendix~\ref{app:ellipse}.

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most major-merging massive galaxies.

    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes more nuanced.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we integrate the profile to a range of radii, and estimate the stellar mass 
    within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation 
            quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the in-situ component
            dominates the \mstar{} within one effective radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            ``in-situ'' phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5).  
            It is worth noting that, at very high-\mstar{} end, there can be 
            significant contribution of accreted stars within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

@@

\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Envelopes}
    \label{ssec:twophase}
